### 2014-07-23 MS.tex
legend fig 4

\texttt{Figure 4.} BiSSE analysis of diversification of nymphalids due
to feeding on Solanaceae hostplants. Speciation and net diversification
rates are significantly higher in Solanaceae feeders (\$lambda\$1, r1).

>>>>

\texttt{Figure 4.} BiSSE analysis of diversification of Solanaceae feeding 
nymphalids shows higher speciation and net diversification
rates in Solanaceae feeders.
